---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library("hadron")
```
```{r}
#' Do a complex division cf1 / cf2, taking real and imaginary part into account
#' (a+bi) / (c+di) = ((a+bi)*(c-di)) / (c^2 + d^2) = ((ac-bd) + (bc-ad)i) / (c^2 + d^2)
complexdivisionvlocal <- function(cf1, cf2){
  stopifnot(inherits(cf1, 'cf_meta'))
  stopifnot(inherits(cf2, 'cf_meta'))
  cf <- cf1
  if(inherits(cf1, 'cf_orig') && inherits(cf2, 'cf_orig')) {
    stopifnot(all(dim(cf1$cf) == dim(cf2$cf)))
    stopifnot(cf1$Time == cf2$Time)


    if( has_icf(cf1) | has_icf(cf2) ){
      stopifnot(has_icf(cf1) & has_icf(cf2))
      divisor <- cf2$cf^2 + cf2$icf^2
      print(head(divisor[, 1:5]))
      print(head(cf1$cf[, 1:5] * cf2$cf[, 1:5]))
      print(head(cf1$icf[, 1:5] * cf2$icf[, 1:5]))
      cf$cf <- (cf1$cf * cf2$cf - cf1$icf * cf2$icf) / divisor
      cf$icf <- (cf1$icf * cf2$cf - cf1$cf * cf2$icf) / divisor
      ## the following is a bit dangerous, however, for
      ## principal correlators this is the only way to
      ## build a ratio
      if(inherits(cf1, 'cf_boot') && inherits(cf2, 'cf_boot') &&
         all(dim(cf1$cf.tsboot$t) == dim(cf2$cf.tsboot$t)) &&
         cf1$seed == cf2$seed && cf1$boot.l == cf2$boot.l) {
        
        divisor <- cf2$cf.tsboot$t^2 + cf2$icf.tsboot$t^2
        divisor0 <- cf2$cf.tsboot$t0^2 + cf2$icf.tsboot$t0^2
        
        cf$cf.tsboot$t  <- (cf1$cf.tsboot$t * cf2$cf.tsboot$t - cf1$icf.tsboot$t * cf2$icf.tsboot$t) / divisor
        cf$cf.tsboot$t0  <- (cf1$cf.tsboot$t0 * cf2$cf.tsboot$t0 - cf1$icf.tsboot$t0 * cf2$icf.tsboot$t0) / divisor0
        
        cf$icf.tsboot$t  <- (cf1$cf.tsboot$t * cf2$icf.tsboot$t - cf1$cf.tsboot$t * cf2$icf.tsboot$t) / divisor
        cf$icf.tsboot$t0  <- (cf1$cf.tsboot$t0 * cf2$icf.tsboot$t0 - cf1$cf.tsboot$t0 * cf2$icf.tsboot$t0) / divisor0
        
        cf$tsboot.se <- apply(cf$cf.tsboot$t, MARGIN = 2L, FUN = cf$error_fn)
        cf$cf0 <- cf$cf.tsboot$t0
        cf$itsboot.se <- apply(cf$icf.tsboot$t, MARGIN = 2L, FUN = cf$error_fn)
        cf$icf0 <- cf$icf.tsboot$t0
      }
    } else {
      cf <- cf1 / cf2
    }
  }
  else cf <- invalidate.samples.cf(cf)
  return (cf)
}


```
```{r}
multiplycfbootstrap <- function(cf, central, bootstraps){
  cfnew <- cf
  cfnew$cf <- cf$cf * central
  if( has_icf(cf)){
    cfnew$icf <- cf$icf * central
  }
  if(inherits(cf, 'cf_boot')){
    cfnew$cf.tsboot$t  <- cf$cf.tsboot$t * bootstraps
    cfnew$cf.tsboot$t0  <- cf$cf.tsboot$t0 * central
    cfnew$tsboot.se <- apply(cfnew$cf.tsboot$t, MARGIN = 2L, FUN = cfnew$error_fn)
    cfnew$cf0 <- cfnew$cf.tsboot$t0
        
    if( has_icf(cf)){
      cfnew$icf.tsboot$t  <- cf$icf.tsboot$t * bootstraps
      cfnew$icf.tsboot$t0  <- cf$icf.tsboot$t0 * central
    
      cfnew$itsboot.se <- apply(cfnew$icf.tsboot$t, MARGIN = 2L, FUN = cfnew$error_fn)
      cfnew$icf0 <- cfnew$icf.tsboot$t0
    }
  }
  return(cfnew)
}
```

Make a filelist
```{r filelist}
filelist <- getorderedfilelist(path="/home/gross/Documents/heavymesons/out_th0/", 
        basename="b", ending="/mes_contr_H_C_S_H")
filelist2 <- getorderedfilelist(path="/home/gross/Documents/heavymesons/out_th0/", 
        basename="a", ending="/mes_contr_H_C_S_H")
filelist <- c(filelist, filelist2)

filelist <- substr(filelist, 1, nchar(filelist[1])-17)

```

Only 199 files, b712 (?) did not run properly, but maybe not worth the time to redo it because the signal is bad anyway
Read in data for vector currents


define function for arbitrary mu, nu
```{r}
##four point function is not symmetric, do not symmetrise, also take care of divison
getcmunu <- function(filellist, Time=128, mu=0, nu=0, boot.R=100, print=FALSE, boot.l=10){
aa <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_A_C_P_H_H_S_H"), Time=Time, 
        corrtype="general", symmetrise=FALSE, sym.vec=c(1), 
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth0_A", mu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("A", nu, "P5", sep="")))
aa <- bootstrap.cf(aa, boot.R=boot.R, boot.l=boot.l)

av <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_V_C_P_H_H_S_H"), Time=Time, 
        corrtype="general", symmetrise=FALSE, sym.vec=c(1), 
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth0_V", mu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("A", nu, "P5", sep="")))
av <- bootstrap.cf(av, boot.R=boot.R, boot.l=boot.l)

va <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_A_C_P_H_H_S_H"), Time=Time, 
        corrtype="general", symmetrise=FALSE, sym.vec=c(1), 
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth0_A", mu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("V", nu, "P5", sep="")))
va <- bootstrap.cf(va, boot.R=boot.R, boot.l=boot.l)

vv <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_V_C_P_H_H_S_H"), Time=Time, 
        corrtype="general", symmetrise=FALSE, sym.vec=c(1), 
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth0_V", mu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("V", nu, "P5", sep="")))
vv <- bootstrap.cf(vv, boot.R=boot.R, boot.l=boot.l)


plusterms <- add.cf(aa, vv)
minusterms <- add.cf(av, va)
cmunu <- add.cf(plusterms, minusterms, a=1., b=-1.)
if(print){
print("vv")
print(vv$cf.tsboot$t0)
print("vv-error")
print(vv$cf.tsboot$se)
print("aa")
print(aa$cf.tsboot$t0)
print("av")
print(av$cf.tsboot$t0)
print("va")
print(va$cf.tsboot$t0)
}

return (cmunu)
}
```



```{r}
#plot(czerozero, log="y")
czerozero <- getcmunu(filellist = filelist, mu=0, nu=0, boot.R=100)
czeroone <- getcmunu(filellist = filelist, mu=0, nu=1, boot.R=100)
# plot(czerozero, xlab="t/a", ylab="C_00(t)", main="C_00")

# coneone <- getcmunu(filellist = filelist, mu=1, nu=1, boot.R=100)
# plot(coneone, xlab="t/a", ylab="C_11(t)", main="C_11")
# conetwo <- getcmunu(filellist = filelist, mu=1, nu=2, boot.R=100)
# plot(conetwo, xlab="t/a", ylab="C_12(t)", main="C_12")
# cthreethree <- getcmunu(filellist = filelist, mu=3, nu=3, boot.R=100, print=TRUE)
# plot(cthreethree, xlab="t/a", ylab="C_33(t)", main="C_33")
# czerothree <- getcmunu(filellist = filelist, mu=0, nu=3, boot.R=100)
# plot(czerothree, xlab="t/a", ylab="C_03(t)", main="C_03")
# cthreezero <- getcmunu(filellist = filelist, mu=3, nu=0, boot.R=100)
# plot(czerothree, xlab="t/a", ylab="C_30(t)", main="C_30")

```

symmetrisation makes 65 timeslices out of 128: measure from 0..127, 0 stays the same, 1+127, 2+126, ..., 64 stays the same -> now frm 0..64, 65 times. Do not symmetrise four-point function, symmetrisation does not make sense with more than one inserted time. But do symmetrise two-point-function to get better signal for mass, matrix element, unsymmetrise later to get values for all timeslices. Calculate smeared-smeared and local-smeared contribution to determine masses, influence of smearing.

```{r}
scalarlocal <- readnissatextcf(filelist, smear_combs_to_read=c("/mes_contr_H_C_S_H"), Time=128,
                corrtype="general", combs_to_read=data.frame(op1_idx="C_H", op2_idx="S_H", spin_comb="P5P5"),
                symmetrise=TRUE, sym.vec=c(1))
scalarlocal <- bootstrap.cf(scalarlocal, boot.R=100, boot.l=10)
scalarsmeared <- readnissatextcf(filelist, smear_combs_to_read=c("/mes_contr_H_C_H_H_S_H"), Time=128,
                corrtype="general", combs_to_read=data.frame(op1_idx="C_H", op2_idx="H_H_S_H", spin_comb="P5P5"),
                symmetrise=TRUE, sym.vec=c(1))
scalarsmeared <- bootstrap.cf(scalarsmeared, boot.R=100, boot.l=10)
scalarsmearedalltimeslices <- unsymmetrise.cf(scalarsmeared)

print(scalarsmeared$cf[1, ])
plot(scalarlocal, log="y", xlab="t/a", ylab="C(t)", main="smeared-smeared two point function")
plot(scalarsmeared, log="y", xlab="t/a", ylab="C(t)", main="smeared-local two point function")
```

get two-point-functions, both smeared-local and smeared-smeared. Determine correlators, use effective mass to get a sense of boundaries for following matrixfit

```{r}
scalarlocaleffmass <- bootstrap.effectivemass(scalarlocal)
scalarsmearedeffmass <- bootstrap.effectivemass(scalarsmeared)
scalarlocaleffmass <- fit.effectivemass(scalarlocaleffmass, t1=10, t2=20)
scalarsmearedeffmass <- fit.effectivemass(scalarsmearedeffmass, t1=14, t2=36)
plot(scalarlocaleffmass, ylim=c(0.79, 0.82), xlab="t/a", ylab="m_eff(t)", main="smeared-local two point function")
plot(scalarsmearedeffmass, ylim=c(0.79, 0.82), xlab="t/a", ylab="m_eff(t)", main="smeared-smeared two point function")
plot(scalarsmearedeffmass, xlab="t/a", ylab="m_eff(t)", main="smeared-smeared two point function")
# print(scalarsmearedeffmass$effMass)
# summary(scalarsmearedeffmass)
```

Do matrixfits to get to $m_c$, $Z$. Fits work only for useCov=FALSE, otherwise 
Error in chol.default(M) : 
  the leading minor of order 20 is not positive definite
```{r}
localmatrix <- matrixfit(scalarlocal, t1=10, t2=20, sym.vec=c("cosh"), useCov=FALSE)
smearmatrix <- matrixfit(scalarsmeared, t1=15, t2=37, sym.vec=c("cosh"), useCov=FALSE)
summary(localmatrix)
summary(smearmatrix)
# plot(smearmatrix)
```


get combined correlator by division
Use eq. 2.8, 2.9, 2.15 to get Y, Z
$\vec{n}=\frac{\vec{q}}{\sqrt{q^2}}=(0,0,1) or (0,0,0)$ for $q=0$?
One possible source of error: /.cf treats real and imaginary part separately, so division is maybe false.

```{r}
# ytwo <- complexdivisionvlocal(czerozero, scalarsmeared)
# plot(ytwo, log="y", xlab="t/a", ylab="Y^2(t)", main="Y^3=M_00")
# print(ytwo$cf.tsboot$t0)
# ytwoeffmass <- bootstrap.effectivemass(ytwo, type="log")
# summary(ytwoeffmass)
# plot(ytwoeffmass)
ytwo <- czerozero / scalarsmearedalltimeslices
mzeroone <- czeroone / scalarsmearedalltimeslices
# plot(ytwo, log="y", xlab="t/a", ylab="Y^2(t)", main="Y^3=M_00")
# print(ytwo)
# combinedone <- coneone / scalarsmeared
# plot(combinedone, log="y", xlab="t/a", ylab="M_11(t)", main="M_11")
# combinedonetwo <- conetwo / scalarsmeared
# plot(combinedonetwo, log="y", xlab="t/a", ylab="M_12(t)", main="M_12")
# ythree <- cthreethree / scalarsmeared
# plot(ythree, log="y", xlab="t/a", ylab="Y^3(t)", main="Y^3=M_33")
# yfour <- (cthreezero + czerothree) / scalarsmeared
# plot(yfour, log="y", xlab="t/a", ylab="Y^4(t)", main="Y^4=M_30 + M_03")
# plot(ytwo + ythree - yfour, log="y", xlab="t/a", ylab="Z^0(t)", main="Z^0 = Y^2 + Y^3 - Y^4")
```

It seems weird that the slope on the logplot is positive, is it supposed to be this way? Was the correlator of the two point function $C(t_1-t_{src})$ taken at the correct times or does there have to be a shift?

Antonio Smeccas Solution for tho0 is monotonously decreasing in the region 0...30.

t2=48 (fixed), t_sink=64, t_src=0, t_1=1...63

For Z, take smeared-smeared matrix element, because correlators in denominator are also smeared. 
Use correlator of potiton 17 to account for the offset caused by t=0 at pos 1.

$t_2=48, t_{sink}=64 \Rightarrow t_{sink}-t_2=16 \Rightarrow C(t_{sink}-t_2)=C_{smeared}(16)$: 

Hadron fits to $0.5\cdot A \cdot A \cdot (\exp(-tm)+\exp(-(time-t)m)$, but in paper we use $Z \cdot (\exp(-tm)+\exp(-(time-t)m)$, so $Z=0.5\cdot A^2$.

```{r}
corrt2_t0 <- scalarsmeared$cf.tsboot$t0[17]
corrt2_t <- scalarsmeared$cf.tsboot$t[, 17]

Z_smear_0 <- smearmatrix$t0[2]^2/2
Z_smear <- smearmatrix$t[, 2]^2/2
Z_smear_0
ytwomul <- multiplycfbootstrap(ytwo, Z_smear_0/corrt2_t0, Z_smear/corrt2_t)
```
```{r}
# print("M00")
# ytwo$cf.tsboot$t0 * Z_smear_0 / corrt2_t0
# ytwomul$cf.tsboot$t0
# 
# (ytwo$cf.tsboot$t0 * Z_smear_0 / corrt2_t0 - ytwomul$cf0) / ytwomul$cf0
# pdf("comparisonjackknifebootstrap.pdf", title="")
plot(ytwomul, log="y", xlim=c(0, 48), xlab="t/a", ylab="M_{0,0}", main="comparison of bootstrapped and jackknifed data", ylim=c(2e-4, 3.5))
datamarco <- read.table("data_marco_m00.csv", header=T, sep=",")
plotwitherror(x=seq(1, 63), y=datamarco$val, dy=datamarco$err, rep=T, col=2, pch=2)
plotwitherror(x=seq(1, 63), y=2*(datamarco$val-ytwomul$cf0[2:64])/(datamarco$val+ytwomul$cf0[2:64]), dy=sqrt((4*ytwomul$cf0[2:64]*datamarco$err/(datamarco$val+ytwomul$cf0[2:64])^2)^2+(4*ytwomul$tsboot.se[2:64]*datamarco$val/(datamarco$val+ytwomul$cf0[2:64])^2)^2), 
         xlab="t/a", ylab=" rel.dev. M_{0,0}", main="relative deviation of bootstrapped and jackknifed data")
plotwitherror(x=seq(1, 63), y=2*(datamarco$val-ytwomul$cf0[2:64])/(datamarco$val+ytwomul$cf0[2:64]), dy=sqrt((4*ytwomul$cf0[2:64]*datamarco$err/(datamarco$val+ytwomul$cf0[2:64])^2)^2+(4*ytwomul$tsboot.se[2:64]*datamarco$val/(datamarco$val+ytwomul$cf0[2:64])^2)^2), ylim=c(-0.5, 0.5), xlab="t/a", ylab=" rel.dev. M_{0,0}", main="relative deviation of bootstrapped and jackknifed data")
lines(x=seq(1, 63), y=rep(0, 63), col=2)
```

$$C_{\mu\nu} \sim J_\muJ_\nu =(V_\mu-A_\mu)(V_\nu-A_\nu)$$

Multiply renormalization factors, C(t2): Multiply bootstrap by bootstrap. Only constant factor, can be done later.

Compute $f_{D_s}$: two combined matrixfit to get to local-local matrix element.

```{r fds matrixfit}
scalar <- concat.cf(scalarlocal, scalarsmeared)
plot(scalar, log="y")
scalarmatrix <- matrixfit(scalar, t1=22, t2=42, 
                          parlist=array(c(1, 1, 2, 2), dim=c(2, 2)), sym.vec=c("cosh", "cosh"), useCov=FALSE, neg.vec=c(1, 1))
plot(scalarmatrix)
summary(scalarmatrix)
fds <- computefps(scalarmatrix, mu1=0.01692, mu2=0.2368, normalisation="new", disprel="lattice")
print(fds)
```

```{r}
scalarsmearedeffmass$effmassfit$t0[1]
scalarsmearedeffmass$effmassfit$se
```

$$
\begin{aligned}
local &\to A_l A_s \exp(-m_c t)\\
smeared &\to A_s A_s \exp(-m_c t)\\
A_l &= \frac{A_l A_s}{\sqrt{A_s A_s}}
\end{aligned}
$$

