---
title: "Getting the results for the Z-Correlators and comparing to those of Antonio"
author: "Christiane"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library("hadron")
source("morefunctions.R")
```

Make a filelist
```{r filelist}
filelist <- getorderedfilelist(path="/home/gross/Documents/heavymesons/out_th0/", 
        basename="b", ending="/mes_contr_H_C_S_H")
filelist2 <- getorderedfilelist(path="/home/gross/Documents/heavymesons/out_th0/", 
        basename="a", ending="/mes_contr_H_C_S_H")
filelist <- c(filelist, filelist2)

filelist <- substr(filelist, 1, nchar(filelist[1])-17)

tsink <- 64
tins <- 48
bootl <- 1
bootsamples <- 199
# print(filelist)

```

Only 199 files, b712 (?) did not run properly, but maybe not worth the time to redo it because the signal is bad anyway.


Read in data for vector currents.


define function for arbitrary $\mu, \nu$.
<!-- In Antonios note, he only mentions AA and VV, so take out mixed parts. -->
AV and VA are only needed for $C_{12}$ and $C_{21}$, not for the rest, so build a switch for them.
The correlators are weighted with renormalization factors.
reformulate Antonios note:

$Y^2(t)=\frac{M_{D_s}}{\exp(M_{D_s}\cdot dt)}\frac{\hat{w}_0^2}{C_2(t)}\left(Z_V^2C_4^{V_0V_0}(t) + Z_A^2C_4^{A_0A_0}(t)\right)$
```{r}
##four point function is not symmetric, do not symmetrise, also take care of division
getcmunu <- function(filellist, Time=128, mu=0, nu=0, boot.R=100, print=FALSE, boot.l=10, ZA, ZV, dZA, dZV, theta = 0, w2 = 1, symmetric=T, unsymmetric=F, sim="fixed"){
if(!symmetric & !unsymmetric){
  stop("getcmunu: at least one of symmetric and unsymmetric has to be given!")
}
if(symmetric){
aa <- readnissatextcf(filelist, smear_combs_to_read=c(paste("mes_contr_H_C_Dth", theta, "_A_C_P_H_H_S_H", sep="")), Time=Time, 
        corrtype="general", symmetrise=FALSE, sym.vec=c(1), 
        # combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth", theta, "_A", mu, "_C_P_H_H_S_H", sep=""), spin_comb="P5P5"))
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth", theta, "_A", nu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("A", mu, "P5", sep="")))
# aa <- bootstrap.cf(aa, boot.R=boot.R, boot.l=boot.l, sim=sim)
aa <- jackknife.cf(aa, boot.l=boot.l)

vv <- readnissatextcf(filelist, smear_combs_to_read=c(paste("mes_contr_H_C_Dth", theta, "_V_C_P_H_H_S_H", sep="")), Time=Time, 
        corrtype="general", symmetrise=FALSE, sym.vec=c(1), 
        # combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth", theta, "_V", mu, "_C_P_H_H_S_H", sep=""), spin_comb="P5P5"))
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth", theta, "_V", nu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("V", mu, "P5", sep="")))
# vv <- bootstrap.cf(vv, boot.R=boot.R, boot.l=boot.l, sim=sim)
vv <- jackknife.cf(vv, boot.l=boot.l)

bootstrapZA <- parametric.bootstrap(boot.R, c(ZA), c(dZA))
bootstrapZV <- parametric.bootstrap(boot.R, c(ZV), c(dZV))
# print(dim(bootstrapZA))
# print(dim(aa$cf.tsboot$t))

aa <- multiplycfbootstrap(cf = aa, central = ZA^2 * w2, bootstraps = bootstrapZA^2 * w2)
vv <- multiplycfbootstrap(cf = vv, central = ZV^2 * w2, bootstraps = bootstrapZV^2 * w2)
plustermsym <- add.cf(aa, vv)
}
  
if(unsymmetric){
av <- readnissatextcf(filelist, smear_combs_to_read=c(paste("mes_contr_H_C_Dth", theta, "_V_C_P_H_H_S_H", sep="")), Time=Time, 
        corrtype="general", symmetrise=FALSE, sym.vec=c(1), 
        # combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth", theta, "_A", mu, "_C_P_H_H_S_H", sep=""), spin_comb="P5P5"))
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth", theta, "_V", nu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("A", mu, "P5", sep="")))
# av <- bootstrap.cf(av, boot.R=boot.R, boot.l=boot.l, sim=sim)
av <- jackknife.cf(av, boot.l=boot.l)

va <- readnissatextcf(filelist, smear_combs_to_read=c(paste("mes_contr_H_C_Dth", theta, "_A_C_P_H_H_S_H", sep="")), Time=Time, 
        corrtype="general", symmetrise=FALSE, sym.vec=c(1), 
        # combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth", theta, "_V", mu, "_C_P_H_H_S_H", sep=""), spin_comb="P5P5"))
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth", theta, "_A", nu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("V", mu, "P5", sep="")))
# va <- bootstrap.cf(va, boot.R=boot.R, boot.l=boot.l, sim=sim)
va <- jackknife.cf(va, boot.l=boot.l)

bootstrapZA <- parametric.bootstrap(boot.R, c(ZA), c(dZA))
bootstrapZV <- parametric.bootstrap(boot.R, c(ZV), c(dZV))
# print(dim(bootstrapZA))
# print(dim(aa$cf.tsboot$t))

av <- multiplycfbootstrap(cf = av, central = ZA*ZV * w2, bootstraps = bootstrapZA*bootstrapZV * w2)
va <- multiplycfbootstrap(cf = va, central = ZV*ZA * w2, bootstraps = bootstrapZV*bootstrapZA * w2)
plustermunsym <- add.cf(av, va)
}


if(print & symmetric){
print("vv")
print(vv$cf.tsboot$t0)
print("vv-error")
print(vv$cf.tsboot$se)
print("aa")
print(aa$cf.tsboot$t0)
}
if(symmetric & unsymmetric){
  res <- add.cf(plustermsym, plustermunsym)
} else if(symmetric){
  res <- plustermsym
} else{
  res <- plustermunsym
}
return (res)
}
```



symmetrisation makes 65 timeslices out of 128: measure from 0..127, 0 stays the same, 1+127, 2+126, ..., 64 stays the same -> now from 0..64, 65 times. Do not symmetrise four-point function, symmetrisation does not make sense with more than one inserted time. But do symmetrise two-point-function to get better signal for mass, matrix element, unsymmetrise later to get values for all timeslices. Calculate smeared-smeared contribution to determine masses.

```{r, echo=FALSE, eval=TRUE}
# scalarlocal <- readnissatextcf(filelist, smear_combs_to_read=c("/mes_contr_H_C_S_H"), Time=128,
#                 corrtype="general", combs_to_read=data.frame(op1_idx="C_H", op2_idx="S_H", spin_comb="P5P5"),
#                 symmetrise=TRUE, sym.vec=c(1))
# scalarlocal <- bootstrap.cf(scalarlocal, boot.R=bootsamples, boot.l=bootl, sim="fixed")
scalarsmeared <- readnissatextcf(filelist, smear_combs_to_read=c("/mes_contr_H_C_H_H_S_H"), Time=128,
                corrtype="general", combs_to_read=data.frame(op1_idx="C_H", op2_idx="H_H_S_H", spin_comb="P5P5"),
                symmetrise=TRUE, sym.vec=c(1))
scalarsmeared <- bootstrap.cf(scalarsmeared, boot.R=bootsamples, boot.l=bootl, sim="fixed")
# , seed=5647382
scalarsmearedalltimeslices <- unsymmetrise.cf(scalarsmeared)

# print(scalarsmeared$cf[1, ])
# plot(scalarlocal, log="y", xlab="t/a", ylab="C(t)", main="smeared-local two point function")
plot(scalarsmeared, log="y", xlab="t/a", ylab="C(t)", main="smeared-smeared two point function")
```

Use effective mass to get a sense of boundaries for following matrixfit.
In the following, use Antonios fitrange, 15-48, everywhere.
Further examination of Antonios data shows that he assigns the ratio of $t, t+1$ to $t+1$, but hadron assigns it to $t$, so Anotnios range $15-48$ corrresponds to $14-47$ in hadron.
<!-- (the matrixfitresuult for 16 to 37 reproduces that of Antonio the most closely.) -->
Goal: reproduce Antonios results for the effective mass

```{r, echo=FALSE, eval=TRUE}
scalarsmearedeffmass <- bootstrap.effectivemass(scalarsmeared, type="solve")
scalarsmearedeffmass <- fit.effectivemass(scalarsmearedeffmass, t1=14, t2=47, useCov=FALSE)
plot(scalarsmearedeffmass, ylim=c(0.79, 0.82), xlab="t/a", ylab="m_eff(t)", main="smeared-smeared two point function")
plot(scalarsmearedeffmass, xlab="t/a", ylab="m_eff(t)", main="smeared-smeared two point function")
# print(scalarsmearedeffmass$effMass)
summary(scalarsmearedeffmass)
# cat("bias:\n", scalarsmearedeffmass$effmassfit$t0[1], "-", mean(scalarsmearedeffmass$effmassfit$t[, 1]), "=", scalarsmearedeffmass$effmassfit$t0[1] - mean(scalarsmearedeffmass$effmassfit$t[, 1]), "\n")
# cat("difference to Antonio:", 0.7999551426 - scalarsmearedeffmass$effmassfit$t0[1])
# scalarlocaleffmass <- bootstrap.effectivemass(scalarlocal, type="solve")
# scalarlocaleffmass <- fit.effectivemass(scalarlocaleffmass, t1=15, t2=48, useCov=TRUE)
# plot(scalarlocaleffmass, ylim=c(0.79, 0.82), xlab="t/a", ylab="m_eff(t)", main="smeared-smeared two point function")
# plot(scalarlocaleffmass, xlab="t/a", ylab="m_eff(t)", main="smeared-smeared two point function")
# # print(scalarsmearedeffmass$effMass)
# summary(scalarlocaleffmass)

```
<!-- seed: 5647382: -->
<!--  0.8000066088 - 0.8000208759 = -1.426709406e-05  -->
<!-- difference to Antonio: -5.146621331e-05 -->

<!-- seed: 987654 -->
<!--  0.8000016698 - 0.8000232463 = -2.15764737e-05  -->
<!-- difference to Antonio: -4.652721124e-05 -->
<!-- seed: 123456 -->
<!--  0.8000027005 - 0.7999757659 = 2.693463372e-05  -->
<!-- difference to Antonio: -4.755792447e-05 -->

Alternative: determine the effective mass via jackknife 

```{r, echo=FALSE}
scalarsmearedjk <- readnissatextcf(filelist, smear_combs_to_read=c("/mes_contr_H_C_H_H_S_H"), Time=128,
                corrtype="general", combs_to_read=data.frame(op1_idx="C_H", op2_idx="H_H_S_H", spin_comb="P5P5"),
                symmetrise=TRUE, sym.vec=c(1))
scalarsmearedjk <- jackknife.cf(scalarsmearedjk, boot.l=bootl)
scalarsmearedjkalltimeslices <- unsymmetrise.cf(scalarsmearedjk)

scalarsmearedjkeffmass <- bootstrap.effectivemass(scalarsmearedjk, type="solve")
scalarsmearedjkeffmass <- fit.effectivemass(scalarsmearedjkeffmass, t1=14, t2=47, useCov=FALSE)
plot(scalarsmearedjkeffmass, ylim=c(0.79, 0.82), xlab="t/a", ylab="m_eff(t)", main="smeared-smeared two point function, jackknife estimators")
plot(scalarsmearedjkeffmass, xlab="t/a", ylab="m_eff(t)", main="smeared-smeared two point function, jackknife estimators")
# print(scalarsmearedeffmass$effMass)
summary(scalarsmearedjkeffmass)
# cat("bias:\n", scalarsmearedjkeffmass$effmassfit$t0[1], "-", mean(scalarsmearedjkeffmass$effmassfit$t[, 1]), "=", scalarsmearedjkeffmass$effmassfit$t0[1] - mean(scalarsmearedjkeffmass$effmassfit$t[, 1]), "\n")
# cat("difference to Antonio:", 0.7999551426 - scalarsmearedeffmass$effmassfit$t0[1])

resultsjackknife <- data.frame(t=scalarsmearedjkeffmass$t.idx, m=scalarsmearedjkeffmass$effMass, dm=scalarsmearedjkeffmass$deffMass)
write.table(resultsjackknife, file="massesjackknife.csv", row.names=F, col.names=T)

```


<!-- Do matrixfits to get to $m_c$, $Z$. Fits work only for useCov=FALSE, otherwise  -->
<!-- Error in chol.default(M) :  -->
<!--   the leading minor of order 20 is not positive definite -->
Now do the matrixfit
```{r, echo=FALSE, eval=TRUE}
# localmatrix <- matrixfit(scalarlocal, t1=10, t2=20, sym.vec=c("cosh"), useCov=FALSE)
smearmatrix <- matrixfit(scalarsmeared, t1=15, t2=48, sym.vec=c("cosh"), useCov=FALSE, parlist = array(c(1,1), dim=c(2,1)), neg.vec = c(1))
# summary(localmatrix)
summary(smearmatrix)
# plot(smearmatrix)
```
<!-- Calculate meff for many different params to see if any of them matches Antonios mass exactly, best result for t1=16, t2=37, but error wrong -->
```{r, echo=FALSE, eval=FALSE}
# tryeffmass <- bootstrap.effectivemass(scalarsmeared, type="solve")
tryeffmass <- bootstrap.effectivemass(scalarsmearedjk, type="solve")
options(digits=10)
resallranges <- data.frame(t1=NA, t2=NA, m=NA, dm=NA, chired=NA, p=NA)
for(t1 in seq(10, 30)){
  for(t2 in seq(max(t1+1, 20), 64)){
    # mfit <- matrixfit(scalarsmeared, t1=t1, t2=t2, sym.vec=c("cosh"), useCov=FALSE, parlist = array(c(1,1), dim=c(2,1)), neg.vec = c(1))
    # cat(t1, " ", t2, " ", mfit$t0[1], " ", mfit$error_fn(mfit$t[,1]), "\n")
    # reseffmass <- fit.effectivemass(tryeffmass, t1=t1, t2=t2)
    # cat(t1, " ", t2, " ", reseffmass$effmassfit$t0[1], " ", reseffmass$effmassfit$se[1], "\n")
    # reseffmass <- fit.effectivemass(scalarsmearedjkeffmass, t1=t1, t2=t2, useCov=T)
    # newlineeffmass <- data.frame(t1=t1, t2=t2, m=reseffmass$effmassfit$t0[1], dm=reseffmass$effmassfit$se[1], chired=reseffmass$chisqr / reseffmass$dof, p=reseffmass$Qval)
    # resallranges <- rbind(resallranges, newlineeffmass)
  }
}
print(resallranges)
# write.table(resallranges, file="resultseffectivemassjackknifeusecovtrue.csv", row.names=F, col.names=T)
```


How to get $w_0$? Here, it is 1. For now, do not take ZA, ZV into account. At a later time, this can easily be changed.
Determine four-point functions:
```{r}
ZA <- 0.74294
dZA <- 0.00024
ZV <- 0.706379
dZV <- 0.000024
ZA <- 1
ZV <- 1
dZA <- 0
dZV <- 0
czerozero <- getcmunu(filellist = filelist, mu=0, nu=0, boot.R=bootsamples, ZA=ZA, ZV=ZV, dZA=dZA, dZV=dZV, w2=1, boot.l=bootl, symmetric=T, unsymmetric=F)
# plot(czerozero, xlab="t/a", ylab="C_00(t)", main="C_00", xlim=c(0, 48), log="y")


```


<!-- y^4 Im(-03+30) -->
<!-- y^5 Re=(IM(12)-IM(21)) / 2 -->
<!-- y^1 11 +22 -->
```{r}
cthreethree <- getcmunu(filellist = filelist, mu=3, nu=3, boot.R=bootsamples, ZA=ZA, ZV=ZV, dZA=dZA, dZV=dZV, w2=1, boot.l=bootl, symmetric=T, unsymmetric=F)
czerothree <- getcmunu(filellist = filelist, mu=0, nu=3, boot.R=bootsamples, ZA=ZA, ZV=ZV, dZA=dZA, dZV=dZV, w2=1, boot.l=bootl, symmetric=T, unsymmetric=F)
cthreezero <- getcmunu(filellist = filelist, mu=3, nu=0, boot.R=bootsamples, ZA=ZA, ZV=ZV, dZA=dZA, dZV=dZV, w2=1, boot.l=bootl, symmetric=T, unsymmetric=F)
coneone <- getcmunu(filellist = filelist, mu=1, nu=1, boot.R=bootsamples, ZA=ZA, ZV=ZV, dZA=dZA, dZV=dZV, w2=1, boot.l=bootl, symmetric=T, unsymmetric=F)
conetwo <- getcmunu(filellist = filelist, mu=1, nu=2, boot.R=bootsamples, ZA=ZA, ZV=ZV, dZA=dZA, dZV=dZV, w2=1, boot.l=bootl, symmetric=F, unsymmetric=T)
ctwoone <- getcmunu(filellist = filelist, mu=2, nu=1, boot.R=bootsamples, ZA=ZA, ZV=ZV, dZA=dZA, dZV=dZV, w2=1, boot.l=bootl, symmetric=F, unsymmetric=T)
ctwotwo <- getcmunu(filellist = filelist, mu=2, nu=2, boot.R=bootsamples, ZA=ZA, ZV=ZV, dZA=dZA, dZV=dZV, w2=1, boot.l=bootl, symmetric=T, unsymmetric=F)
```


<!-- is dt t_sink - t_j > 0  or t_j-t_sink < 0? -->
<!-- here, $\hat{w}_0=1$. -->
Determine prefactor for the H-tensors including bootstraps: $\frac{m_{D_s}}{\exp(m_{D_s} \cdot dt)}\cdot \frac{1}{C_2}$
For now, take mass from bootstrapfit, to match the resampling procedure for $C_4$.
```{r}
# mds <- c(smearmatrix$t0[1], smearmatrix$t[,1])
# mds <- c(scalarsmearedeffmass$effmassfit$t0[1], scalarsmearedeffmass$effmassfit$t[,1])
mds <- c(scalarsmearedjkeffmass$effmassfit$t0[1], scalarsmearedjkeffmass$effmassfit$t[,1])
dt <- tins-tsink
expmdsdt <- exp(mds*dt)
mdsoverexpmdsdt <- mds / expmdsdt
expovermds <- expmdsdt / mds
# denom <- multiplycfbootstrap(scalarsmearedalltimeslices, expovermds[1], expovermds[2:length(mds)])
denom <- multiplycfbootstrap(scalarsmearedjkalltimeslices, expovermds[1], expovermds[2:length(mds)])
```



<!-- Maybe the problem is in the division of the imaginary parts? So far, always did complex division or divided real by real and imaginary by imaginary, but try to divide imaginary be real for yfour. -->
<!-- Antonio only ever uses the real part of C_2 -->
Determine $Y$ and $Z$ from the data.
```{r}
yone <- coneone+ctwotwo
yfour <- multiplycfscalar(czerothree+cthreezero, 0.5)
yfive <- conetwo-ctwoone

yone <- dividebyreal.cf(multiplycfscalar(yone, 0.5), denom)
ytwo <- dividebyreal.cf(czerozero, denom)
ythree <- dividebyreal.cf(multiplycfscalar(cthreethree, -1), denom)
yfour <- dividebyreal.cf(multiplycfscalar(yfour, -1), denom)
yfive <- dividebyreal.cf(multiplycfscalar(yfive, 0.5), denom)


```
```{r}
data_christiane <- data.frame(t=seq(0,127), 
c4=czerozero$cf0, dc4=czerozero$tsboot.se, 
c2=scalarsmearedalltimeslices$cf0, dc2=scalarsmearedalltimeslices$tsboot.se)

data_christiane$ytwo = c(ytwo$cf0[(tins+1):1], rep(NA, 127-tins)) 
data_christiane$dy2=c(ytwo$tsboot.se[(tins+1):1], rep(NA, 127-tins))
data_christiane$yone <- c(yone$cf0[(tins+1):1], rep(NA, 127-tins))
data_christiane$dy1 <- c(yone$tsboot.se[(tins+1):1], rep(NA, 127-tins))
data_christiane$ythree <- c(ythree$cf0[(tins+1):1], rep(NA, 127-tins))
data_christiane$dy3 <- c(ythree$tsboot.se[(tins+1):1], rep(NA, 127-tins))
data_christiane$yfour <- c(yfour$icf0[(tins+1):1], rep(NA, 127-tins))
data_christiane$dy4 <- c(yfour$itsboot.se[(tins+1):1], rep(NA, 127-tins))
data_christiane$yfive <- c(yfive$icf0[(tins+1):1], rep(NA, 127-tins))
data_christiane$dy5 <- c(yfive$itsboot.se[(tins+1):1], rep(NA, 127-tins))

data_christiane$zzero <- data_christiane$ytwo + data_christiane$ythree - 2 * data_christiane$yfour 
data_christiane$dzzero <- sqrt(data_christiane$dy2^2 + data_christiane$dy3^2 + 4 * data_christiane$dy4^2)
data_christiane$zone <- - 4 * data_christiane$yone + 2 * data_christiane$ythree - 2 * data_christiane$yfour 
data_christiane$dzone <- sqrt(16 * data_christiane$dy1^2 + 4 * data_christiane$dy3^2 + 4 * data_christiane$dy4^2)
data_christiane$ztwo <- data_christiane$ythree - 2 * data_christiane$yone 
data_christiane$dztwo <- sqrt(data_christiane$dy3^2 + 4 * data_christiane$dy1^2)
write.table(data_christiane, "correlators_christiane_th0_tins48.csv", row.names=F, col.names=T)
```

```{r, echo=FALSE, eval=TRUE}
dataantonio <- read.table("Antonio_Jackknife/z0_iset0.dat", header=F, col.names = c("t", "Z0", "dZ0", "Z1", "dZ1", "Z2", "dZ2"))
# dataantonio <- read.table("z0_iset0_antonio.dat", header=F, col.names = c("t", "Z0", "dZ0", "Z1", "dZ1", "Z2", "dZ2"))
```

compare masses to Antonio: masses fit very well, for result from smeared correlator deviation seems to be about machine precision (between 3e-15 for t=1 and 5e-37 for t=64). 
The results from the matrix fit are not symmetrised, so the deviation jumps to 8e-4 for t=65. 
However, for the determination of the mass we are only interested in t in (0, 64), so this does not matter. 
Comparison with the resymmetrised results shows the deviation is about machine precision even for t>64.
This is true for bootstraps and jackknifed data.
The effective mass results of the jackknife match up well:
Christianes effective mass is `r scalarsmearedjkeffmass$effmassfit$t0[1]` $\pm$ `r scalarsmearedjkeffmass$effmassfit$se[1]`, Antonios is $7.9995453694e-01 \pm 1.9349795130e-04$.
<!-- [1] 0.7999553 -->
<!-- [1] 0.0001915896 -->
So the deviation between the means is $7.43e-07$, or $0.4\%$ of the errors, and the deviation between the errors is $1.91e-06$, $1\%$ of the errors.

```{r , echo=FALSE, eval=TRUE}
data_a_mass <- read.table("Antonio_Jackknife/H_iset0.dat", header=FALSE, nrow=64)
# data_a_mass <- read.table("H_iset0_antonio_2.dat", header=FALSE)
# length(data_a_mass$V1)#, col.names = ("t", "m", "dm", "V4", "V5", "V6", "V7"))
# plotwitherror(x=data_a_mass$V1[1:128], y=data_a_mass$V2[1:128]-smearmatrix$CF$Cor[1:128], dy=sqrt(data_a_mass$V3[1:128]**2+smearmatrix$CF$Cor[1:128]**2), main= "C_2 antonio vs christiane (from matrixfit used for determining effmass)", xlim=c(0, 65), ylim=c(-3e-15, 3e-15), xlab="t/a", ylab="deviation m_eff")
# plotwitherror(x=data_a_mass$V1[1:128], y=2*(data_a_mass$V2[1:128]-smearmatrix$CF$Cor[1:128])/(data_a_mass$V2[1:128]+smearmatrix$CF$Cor[1:128]), main= "C_2 antonio vs christiane matrixfit, relative deviation (difference over mean)", xlim=c(0, 65), xlab="t/a", ylab="relative deviation m_eff")
# plotwitherror(x=data_a_mass$V1[1:64], y=data_a_mass$V2[1:64]-scalarsmearedalltimeslices$cf0[1:64], dy=sqrt(data_a_mass$V3[1:64]^2+scalarsmearedalltimeslices$tsboot.se[1:64]^2), ylim=c(-1e-18, 1e-18), main="C_2 antonio vs christiane(from re-symmetrised effective mass fit")
# plotwitherror(x=data_a_mass$V1[1:64], y=abs(data_a_mass$V2[1:64]-scalarsmearedalltimeslices$cf0[1:64]), dy=sqrt(data_a_mass$V3[1:64]^2+scalarsmearedalltimeslices$tsboot.se[1:64]^2), log="y", main="abs value C_2 antonio vs christiane(from re-symmetrised effective mass fit", ylim=c(1e-38, 1e-14))
# plotwitherror(x=data_a_mass$V1[1:64], y=data_a_mass$V2[1:64]-scalarsmearedjkalltimeslices$cf0[1:64], dy=sqrt(data_a_mass$V3[1:64]^2+scalarsmearedjkalltimeslices$tsboot.se[1:64]^2), ylim=c(-1e-18, 1e-18), main="C_2 antonio vs christiane(from re-symmetrised effective mass fit")
plotwitherror(x=data_a_mass$V1[1:64], y=abs(data_a_mass$V2[1:64]-scalarsmearedjkalltimeslices$cf0[1:64]), dy=sqrt(data_a_mass$V3[1:64]^2+scalarsmearedjkalltimeslices$tsboot.se[1:64]^2), log="y", main="abs value C_2 antonio vs christiane(from re-symmetrised effective mass fit", ylim=c(1e-38, 1e-14))

plotwitherror(x=data_a_mass$V1[2:63], y=abs(data_a_mass$V4[2:63]-scalarsmearedjkeffmass$effMass[1:62]), 
              dy=sqrt((data_a_mass$V5[2:63])^2+(scalarsmearedjkeffmass$deffMass[1:62])^2), 
              log="y", ylim=c(1e-8, 2e-2), xlab="t/a", ylab="Delta m_eff", main="deviation effective masses")

print(data_a_mass$V4[2:64]-scalarsmearedjkeffmass$effMass[1:63])
print(data_a_mass$V4[2:64])

# print(data_a_mass$V2-smearmatrix$CF$Cor)
# print(data_a_mass$V2-scalarsmearedalltimeslices$cf0)
# print(data_a_mass$V2-scalarsmeared$cf0)
```

Compare Z Antonio and Christiane. At first glance, the results match up very well, however when zooming in we see that there are some slight deviations, very well contained within the errors.
The deviations of the means are all below 1e-03 of the errors, the deviations of the errors is up to ten times as large as the deviation of the means, but still the relative deviations are below $10\%$.
the relative deviations of the means are within 1e-04.
<!-- The relative deviations (difference over mean of the results) are smaller than 1e-4. -->

```{r, echo=FALSE, eval=TRUE}
# pdf("compareZeffmasssolve.pdf", title="")
plotwitherror(x=seq(1, 48), y=dataantonio$Z0[2:49], dy=dataantonio$dZ0[2:49], xlab="t", ylab="Z^0", main="Z^0 by Antonio and Christiane", log="y")
plotwitherror(x=seq(1, 48), y=data_christiane$zzero[2:49], dy=data_christiane$dzzero[2:49], col=2, pch=2, rep=TRUE)
  legend(x="topright", legend=c("Antonio", "Christiane"), col=c(1, 2), pch=c(1, 2))
plotwitherror(x=seq(1, 48), y=dataantonio$Z1[2:49], dy=dataantonio$dZ1[2:49], xlab="t", ylab="Z^1", main="Z^1 by Antonio and Christiane", log="y")
plotwitherror(x=seq(1, 48), y=data_christiane$zone[2:49], dy=data_christiane$dzone[2:49], col=2, pch=2, rep=TRUE)
  legend(x="topright", legend=c("Antonio", "Christiane"), col=c(1, 2), pch=c(1, 2))
plotwitherror(x=seq(1, 48), y=dataantonio$Z2[2:49], dy=dataantonio$dZ2[2:49], xlab="t", ylab="Z^2", main="Z^2 by Antonio and Christiane", log="y")
plotwitherror(x=seq(1, 48), y=data_christiane$ztwo[2:49], dy=data_christiane$dztwo[2:49], col=2, pch=2, rep=TRUE)
  legend(x="topright", legend=c("Antonio", "Christiane"), col=c(1, 2), pch=c(1, 2))

plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$zzero[1:49]+dataantonio$Z0[1:49]), dy=sqrt(data_christiane$dzzero[1:49]^2+dataantonio$dZ0[1:49]^2), main="Z_0 antonio vs Z_0 christiane", ylim=c(-1e-4, 1e-4), xlab="t", ylab="deviation")
lines(x=seq(-10, 58), y=rep(0, 69))
plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$zone[1:49]+dataantonio$Z1[1:49]), dy=sqrt(data_christiane$dzone[1:49]^2+dataantonio$dZ1[1:49]^2), main="Z_1 antonio vs Z_1 christiane", ylim=c(-1e-4, 1e-4), xlab="t", ylab="deviation")
lines(x=seq(-10, 58), y=rep(0, 69))
plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$ztwo[1:49]+dataantonio$Z2[1:49]), dy=sqrt(data_christiane$dztwo[1:49]^2+dataantonio$dZ2[1:49]^2), main="Z_2 antonio vs Z_2 christiane", ylim=c(-1e-4, 1e-4), xlab="t", ylab="deviation")
lines(x=seq(-10, 58), y=rep(0, 69))

#
plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$dzzero[1:49]+dataantonio$dZ0[1:49]), main="errors Z_0 antonio vs errors Z_0 christiane", xlab="t", ylab="deviation of errors")
lines(x=seq(-10, 58), y=rep(0, 69))
# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$dzone[1:49]+dataantonio$dZ1[1:49]), main="errors Z_1 antonio vs errors Z_1 christiane", xlab="t", ylab="deviation of errors")
# lines(x=seq(-10, 58), y=rep(0, 69))
# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$dztwo[1:49]+dataantonio$dZ2[1:49]), main="errors Z_2 antonio vs errors Z_2 christiane", xlab="t", ylab="deviation of errors")
# lines(x=seq(-10, 58), y=rep(0, 69))
# 

plotwitherror(x=dataantonio$t[1:49], y=2*(-data_christiane$dzzero[1:49]+dataantonio$dZ0[1:49])/(+data_christiane$dzzero[1:49]+dataantonio$dZ0[1:49]), main="errors Z_0 antonio vs errors Z_0 christiane", xlab="t", ylab="relative deviation of errors")
lines(x=seq(-10, 58), y=rep(0, 69))

plotwitherror(x=dataantonio$t[1:49], y=2*(-data_christiane$dzone[1:49]+dataantonio$dZ1[1:49])/(+data_christiane$dzone[1:49]+dataantonio$dZ1[1:49]), main="errors Z_0 antonio vs errors Z_0 christiane", xlab="t", ylab="relative deviation of errors")
lines(x=seq(-10, 58), y=rep(0, 69))

plotwitherror(x=dataantonio$t[1:49], y=2*(-data_christiane$dztwo[1:49]+dataantonio$dZ2[1:49])/(+data_christiane$dztwo[1:49]+dataantonio$dZ2[1:49]), main="errors Z_0 antonio vs errors Z_0 christiane", xlab="t", ylab="relative deviation of errors")
lines(x=seq(-10, 58), y=rep(0, 69))

plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$zzero[1:49]+dataantonio$Z0[1:49])/dataantonio$dZ0[1:49],  main="Z_0 antonio vs Z_0 christiane, deviation over error", xlab="t", ylab="deviation")
lines(x=seq(-10, 58), y=rep(0, 69))
# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$zone[1:49]+dataantonio$Z1[1:49])/dataantonio$dZ1[1:49],  main="Z_1 antonio vs Z_1 christiane, deviation over error", xlab="t", ylab="deviation")
# lines(x=seq(-10, 58), y=rep(0, 69))
# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$ztwo[1:49]+dataantonio$Z2[1:49])/dataantonio$dZ1[1:49],  main="Z_2 antonio vs Z_2 christiane, deviation over error", xlab="t", ylab="deviation")
# lines(x=seq(-10, 58), y=rep(0, 69))

# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$zone[1:49]+dataantonio$Z1[1:49])/(-data_christiane$dzzero[1:49]+dataantonio$dZ0[1:49]),  main="Z_1 antonio vs Z_1 christiane, deviation over deviation errors", xlab="t", ylab="deviation")
# lines(x=seq(-10, 58), y=rep(0, 69))
# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$ztwo[1:49]+dataantonio$Z2[1:49])/(-data_christiane$dzzero[1:49]+dataantonio$dZ0[1:49]),  main="Z_2 antonio vs Z_2 christiane, deviation over deviation errors", xlab="t", ylab="deviation")
# lines(x=seq(-10, 58), y=rep(0, 69))
# 
# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$zzero[1:49]+dataantonio$Z0[1:49]), dy=sqrt(data_christiane$dzzero[1:49]^2+dataantonio$dZ0[1:49]^2), main="Z_0 antonio vs Z_0 christiane", ylim=c(-1e-6, 1e-6), xlab="t", ylab="deviation")
# lines(x=seq(-10, 58), y=rep(0, 69))
# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$zone[1:49]+dataantonio$Z1[1:49]), dy=sqrt(data_christiane$dzone[1:49]^2+dataantonio$dZ1[1:49]^2), main="Z_1 antonio vs Z_1 christiane", ylim=c(-1e-6, 1e-6), xlab="t", ylab="deviation")
# lines(x=seq(-10, 58), y=rep(0, 69))
# plotwitherror(x=dataantonio$t[1:49], y=(-data_christiane$ztwo[1:49]+dataantonio$Z2[1:49]), dy=sqrt(data_christiane$dztwo[1:49]^2+dataantonio$dZ2[1:49]^2), main="Z_2 antonio vs Z_2 christiane", ylim=c(-1e-6, 1e-6), xlab="t", ylab="deviation")
# lines(x=seq(-10, 58), y=rep(0, 69))

ylim <- c(-1e-4, 1e-4)
plotwitherror(x=dataantonio$t[1:49], y=2*(-data_christiane$zzero[1:49]+dataantonio$Z0[1:49])/(dataantonio$Z0[1:49]+data_christiane$zzero[1:49]), main="relative deviation Z_0 antonio vs Z_0 christiane (difference over mean)", xlab="t", ylab="deviation", ylim=ylim)
lines(x=seq(-10, 58), y=rep(0, 69))
plotwitherror(x=dataantonio$t[1:49], y=2*(-data_christiane$zone[1:49]+dataantonio$Z1[1:49])/(dataantonio$Z0[1:49]+data_christiane$zzero[1:49]), main="relative deviation Z_1 antonio vs Z_1 christiane (difference over mean)", ylim=ylim, xlab="t", ylab="deviation")
lines(x=seq(-10, 58), y=rep(0, 69))
plotwitherror(x=dataantonio$t[1:49], y=2*(-data_christiane$ztwo[1:49]+dataantonio$Z2[1:49])/(dataantonio$Z0[1:49]+data_christiane$zzero[1:49]), main="relative deviation Z_2 antonio vs Z_2 christiane (difference over mean)", ylim=ylim, xlab="t", ylab="deviation")
lines(x=seq(-10, 58), y=rep(0, 69))
```

Summary of all Ys, with factors, im, real used
```{r, echo=FALSE, eval=TRUE}
summary <- data.frame(
  corr = c("Y1", "Y2", "Y3", "Y4", "Y5"),
  indices = c("11+22", "00", "-33", "-1/2*(03+30)", "1/2*(12-21)"),
  realpart =  c("RE", "RE", "RE", "IM", "IM"), 
  AAplusVV = c(T, T, T, T, F),
  AVplusVA = c(F, F, F, F, T),
  additionalfactor = c(0.5, 1, 1, 1, 1)
)
knitr::kable(summary)
```

Antonio wrote that the additional factor $\frac{1}{2}$ in $Y^1$ comes from the fact that the contribution is equally split between two unit vectors.  This is not the case for the other $Y$.
The factor $\frac{1}{2}$ in $Y^4$ and $Y^5$ comes from the paper.