---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
library("hadron")
```

Make a filelist
```{r filelist}
filelist <- getorderedfilelist(path="/home/gross/Documents/heavymesons/out_th0/", 
        basename="b", ending="/mes_contr_H_C_S_H")
filelist2 <- getorderedfilelist(path="/home/gross/Documents/heavymesons/out_th0/", 
        basename="a", ending="/mes_contr_H_C_S_H")
filelist <- c(filelist, filelist2)

filelist <- substr(filelist, 1, nchar(filelist[1])-17)

```

Only 199 files, b712 (?) did not run properly, but maybe not worth the time to redo it because the signal is bad anyway
Read in data for vector currents

```{r readvectorcurrent}
aa <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_A_C_P_H_H_S_H"), Time=128, 
        corrtype="newcorr", combs_to_read=data.frame(op1_idx="C_H", op2_idx="Dth0_A0_C_P_H_H_S_H", spin_comb="A0P5"),
        symmetrise=TRUE, sym.vec=c(1))
aa <- bootstrap.cf(aa, boot.R=20)

av <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_V_C_P_H_H_S_H"), Time=128, 
        corrtype="newcorr", combs_to_read=data.frame(op1_idx="C_H", op2_idx="Dth0_V0_C_P_H_H_S_H", spin_comb="A0P5"),
        symmetrise=TRUE, sym.vec=c(1))
av <- bootstrap.cf(av, boot.R=20)

va <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_A_C_P_H_H_S_H"), Time=128, 
        corrtype="newcorr", combs_to_read=data.frame(op1_idx="C_H", op2_idx="Dth0_A0_C_P_H_H_S_H", spin_comb="V0P5"),
        symmetrise=TRUE, sym.vec=c(1))
va <- bootstrap.cf(va, boot.R=20)

vv <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_V_C_P_H_H_S_H"), Time=128, 
        corrtype="newcorr", combs_to_read=data.frame(op1_idx="C_H", op2_idx="Dth0_V0_C_P_H_H_S_H", spin_comb="V0P5"),
        symmetrise=TRUE, sym.vec=c(1))
vv <- bootstrap.cf(vv, boot.R=20)

```

Combine to one big correlatorand determine effective mass

```{r combinecf}
plusterms <- add.cf(aa, vv)
minusterms <- add.cf(av, va)
czerozero <- add.cf(plusterms, minusterms, a=1., b=-1.)
effmass <- bootstrap.effectivemass(czerozero, type="solve")

```


plot results
```{r plot1}

pdf("tryreadin.pdf", title="")
plot(aa, log="y", main="AA", xlab="t/a", ylab="A_0A_0")
plot(av, log="y", main="AV", xlab="t/a", ylab="A_0V_0")
plot(va, log="y", main="VA", xlab="t/a", ylab="V_0A_0")
plot(vv, log="y", main="VV", xlab="t/a", ylab="V_0V_0")
plot(czerozero, log="y")
plot(effmass)

```

define function for arbitrary mu, nu
```{r}
getcmunu <- function(filellist, Time=128, mu=0, nu=0, boot.R=100){
aa <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_A_C_P_H_H_S_H"), Time=Time, 
        corrtype="newcorr", symmetrise=TRUE, sym.vec=c(1), 
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth0_A", nu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("A", mu, "P5", sep="")))
aa <- bootstrap.cf(aa, boot.R=boot.R)

av <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_V_C_P_H_H_S_H"), Time=Time, 
        corrtype="newcorr", symmetrise=TRUE, sym.vec=c(1), 
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth0_V", nu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("A", mu, "P5", sep="")))
av <- bootstrap.cf(av, boot.R=boot.R)

va <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_A_C_P_H_H_S_H"), Time=Time, 
        corrtype="newcorr", symmetrise=TRUE, sym.vec=c(1), 
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth0_A", nu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("V", mu, "P5", sep="")))
va <- bootstrap.cf(va, boot.R=boot.R)

vv <- readnissatextcf(filelist, smear_combs_to_read=c("mes_contr_H_C_Dth0_V_C_P_H_H_S_H"), Time=Time, 
        corrtype="newcorr", symmetrise=TRUE, sym.vec=c(1), 
        combs_to_read=data.frame(op1_idx="C_H", op2_idx=paste("Dth0_V", nu, "_C_P_H_H_S_H", sep=""), spin_comb=paste("V", mu, "P5", sep="")))
vv <- bootstrap.cf(vv, boot.R=boot.R)


plusterms <- add.cf(aa, vv)
minusterms <- add.cf(av, va)
cmunu <- add.cf(plusterms, minusterms, a=1., b=-1.)
return (cmunu)
}
```



```{r}
#plot(czerozero, log="y")
plot(getcmunu(filellist = filelist, mu=0, nu=0, boot.R=20), log="y")

```

```{r}
scalarlocal <- readnissatextcf(filelist, smear_combs_to_read=c("/mes_contr_H_C_S_H"), Time=128,
                corrtype="newcorr", combs_to_read=data.frame(op1_idx="C_H", op2_idx="S_H", spin_comb="P5P5"),
                symmetrise=TRUE, sym.vec=c(1))
scalarlocal <- bootstrap.cf(scalarlocal, boot.R=20)
scalarsmeared <- readnissatextcf(filelist, smear_combs_to_read=c("/mes_contr_H_C_H_H_S_H"), Time=128,
                corrtype="newcorr", combs_to_read=data.frame(op1_idx="C_H", op2_idx="H_H_S_H", spin_comb="P5P5"),
                symmetrise=TRUE, sym.vec=c(1))
scalarsmeared <- bootstrap.cf(scalarsmeared, boot.R=20)
plot(scalarlocal, log="y")
plot(scalarsmeared, log="y")
```
get two-point-functions, both smeared-local and smeared-smeared. Determine correlators, use effective mass to get a sense of boundaries forfollowing matrixfit

```{r}
scalarlocaleffmass <- bootstrap.effectivemass(scalarlocal)
scalarsmearedeffmass <- bootstrap.effectivemass(scalarsmeared)
plot(scalarlocaleffmass, ylim=c(0.79, 0.82))
plot(scalarsmearedeffmass, ylim=c(0.79, 0.82))
scalarlocaleffmass <- fit.effectivemass(scalarlocaleffmass, t1=20, t2=44)
scalarsmearedeffmass <- fit.effectivemass(scalarsmearedeffmass, t1=14, t2=42)
plot(scalarlocaleffmass, ylim=c(0.79, 0.82))
plot(scalarsmearedeffmass, ylim=c(0.79, 0.82))
```
Do matrixfits to get to $m_c$, $Z$. Fits work only for useCov=FALSE, otherwise 
Error in chol.default(M) : 
  the leading minor of order 20 is not positive definite
```{r}
localmatrix <- matrixfit(scalarlocal, t1=22, t2=44, sym.vec=c("cosh"), useCov=FALSE)
smearmatrix <- matrixfit(scalarsmeared, t1=14, t2=42, sym.vec=c("cosh"), useCov=FALSE)
summary(localmatrix)
summary(smearmatrix)
```

$$
\begin{aligned}
local &\to A_l A_s \exp(-m_c t)\\
smeared &\to A_s A_s \exp(-m_c t)\\
A_l &= \frac{A_l A_s}{\sqrt{A_s A_s}}
\end{aligned}
$$
$t_2=48, t_{sink}=64 \Rightarrow t_{sink}-t_2=16 \Rightarrow C(t_{sink}-t_2)=C_{smeared}(16)$: 
```{r}
localamplitude_t0 <- localmatrix$t0[2]/sqrt(smearmatrix$t0[2])
localamplitude_t <- localmatrix$t[,2]/sqrt(smearmatrix$t[,2])

# localamplitude_t0
# localamplitude_t
# localmatrix$error_fn(localamplitude_t0)

corrt2_t0 <- scalarsmeared$cf.tsboot$t0[16]
corrt2_t <- scalarsmeared$cf.tsboot$t[, 16]

# corrt2_t0
# corrt2_t

prefactor_t0 <- localamplitude_t0 / corrt2_t0
prefactor_t <- localamplitude_t / corrt2_t

prefactor_t0
```

get combined correlator by division
```{r}
combined <- czerozero / scalarsmeared
plot(combined, log="y")
```
t2=48 (fixed), t_sink=64, t_src=0, t_1=1...63

$C_{\mu\nu} \sim J_\muJ_\nu =(V_\mu-A_\mu)(V_\nu-A_\nu)$

Multiply renormalization factors, C(t2): Multiply bootstrap by bootstrap. Only constant factor, can be done later.

```{r multiply bootstrap}

```




