---
title: "analyse pion E112"
author: "Christiane"
date: "2024-04-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("hadron")
```

```{r}
# After preprocessing the data for the mesons, ... we have the real 
# and imaginary parts of the correlators in one file each. 
# We read those into a cf object.
# the imaginary data need not be given.

readcffrompreprocessed <- function (realfile, path  = "", imfile="", im=F) {
  ## determine number of measurements
  nmeas <- read.table(paste0(path, realfile), nrows=1)
  Time <- nmeas$V2
  confno <- nmeas$V1
  dat <- read.table(paste0(path, realfile), skip=1)
  tmp <- matrix(data=dat$V2, nrow=Time, ncol=confno)
  # print(nmeas)
  #~   print(tmp)
  Dm <- dim(tmp)
  ret <- cf_meta(nrObs = 1, Time =  Time, nrStypes = 1)
  if (im==F) ret <- cf_orig(ret, cf = t(tmp))
  if (im==T) {
    stopifnot(file.exists(paste0(path, imfile)))
    datim <- read.table(paste0(path, imfile), skip=1)
    tmpim <- matrix(data=datim$V2, nrow=Time, ncol=confno)
    ret <- cf_orig(ret, cf = t(tmp), icf=t(tmpim))
  }
  ret$conf.index <- confno
  ret <- symmetrise.cf(ret)
  
  return(invisible(ret))
}


## cdf needed for determining mean, intervals with AIC
cdf <- function(y, means, sds, weights) {
  num <- sum(weights * pnorm(y, means, sds))
  den <- sum(weights)
  return(num / den)
}

## cdf - quantile, needed for uniroot

AICquantile <- function(y, means, sds, weights, quantile) cdf(y, means, sds, weights) - quantile

## apply requires the argument to be iterated over in first place
getquantile <- function(means, sds, weights, quantile, interval) {
  root <- try(uniroot(f = AICquantile, quantile = quantile, means = means, sds = sds,
                      weights = weights, interval = interval, tol = 1e-12))
  if (inherits(root, "try-error")) {
    res <- NA
  } else {
    res <- root$root
  }
  return(res)
}


## determine effective mass with the Akaike Information Criterion
deteffmassaic <- function(effmass, start = 1, mindistance = 2, verbose = FALSE) {
  ## additional parameters for saving, plotting
  # discard all points which are less than one sigma away from zero or have negative mass
  effmassall <- effmass
  for (time in effmass$t.idx) {
    if(is.na(effmass$effMass[time]) || abs(effmass$effMass[time] / effmass$deffMass[time]) < 1.0 || effmass$effMass[time] < 0) {
      if(verbose) print(paste("removing timeslice ", time, "due to being too close to zero"))
      effmass$effMass[time] <- NA
      effmass$deffMass[time] <- NA
      effmass$effMass.tsboot[, time] <- rep(NA, effmass$boot.R)
      effmass$t0[time] <- NA
      effmass$se[time] <- NA
      effmass$t[, time] <- rep(NA, effmass$boot.R)
    }
  }
  ntimeslices <- length(effmass$t.idx)
  ncombs <- 0.5 * (ntimeslices - mindistance - start - 1) * (ntimeslices - mindistance - start)
  weights <- rep(NA, ncombs)
  masses <- rep(NA, ncombs)
  sds <- rep(NA, ncombs)
  bootstraps <- array(NA, dim = c(effmass$boot.R, ncombs))
  savefits <- data.frame(index = NA, t1 = NA, t2 = NA,
                         m = NA, dm = NA, chisqr = NA, p = NA, weight = NA)
  index <- 1
  for (t1 in seq(start, ntimeslices - mindistance - 2)) {
    for (t2 in seq(t1 + mindistance, ntimeslices - 2)) {
      # cat("i = ", index, " t1 = ", t1, " t2 = ", t2, "\n")
      tmp <- try(fit.effectivemass(effmass, t1 = t1, t2 = t2, useCov = TRUE))
      if (!inherits(tmp, "try-error")) {
        weights[index] <- exp(-0.5 * (tmp$chisqr + 2 - (t2 - t1)))
        masses[index] <- tmp$effmassfit$t0[1]
        sds[index] <- tmp$effmassfit$se[1]
        bootstraps[, index] <- tmp$effmassfit$t[, 1]
        newline <- data.frame(index = index, t1 = t1, t2 = t2,
                              m = tmp$effmassfit$t0[1], dm = tmp$effmassfit$se[1],
                              chisqr = tmp$chisqr, p = tmp$Qval, weight = weights[index])
        savefits <- rbind(savefits, newline)
      } else {
        weights[index] <- 0
        masses[index] <- 0
        sds[index] <- 0
        bootstraps[, index] <- rep(0, effmass$boot.R)
        cat("there was a problem with t1 = ", t1, ", t2 = ", t2, "\n")
      }
      index <- index + 1
    }
  }
  savefits <- savefits[-1, ]
  
  # failsafe if no fit succeeds
  if(length(savefits$index) == 0) return(list(FALSE, FALSE, FALSE, FALSE))
  
  savefits$weight <- savefits$weight / sum(savefits$weight)
  interval <- c(0.9 * min(bootstraps), 1.1 * max(bootstraps))
  
  resmass <- uniroot(f = AICquantile, quantile = 0.5, means = masses, sds = sds,
                     weights = weights, interval = interval, tol = 1e-12)
  res16 <- uniroot(f = AICquantile, quantile = 0.16, means = masses, sds = sds,
                   weights = weights, interval = interval, tol = 1e-12)
  res84 <- uniroot(f = AICquantile, quantile = 0.84, means = masses, sds = sds,
                   weights = weights, interval = interval, tol = 1e-12)
  
  resmasserr <- abs(0.5 * (res84$root - res16$root))
  
  bootmass <- apply(X = bootstraps, MARGIN = 1, FUN = getquantile, sds = sds,
                    weights = weights, quantile = 0.5, interval = interval)
  boot16 <- apply(X = bootstraps, MARGIN = 1, FUN = getquantile, sds = sds,
                  weights = weights, quantile = 0.16, interval = interval)
  boot84 <- apply(X = bootstraps, MARGIN = 1, FUN = getquantile, sds = sds,
                  weights = weights, quantile = 0.84, interval = interval)
  
  bootmean <- mean(bootmass, na.rm = T)
  booterrstat <- sd(bootmass, na.rm = T)
  booterrtot <- abs(0.5 * (mean(boot84, na.rm = T) - mean(boot16, na.rm = T)))
  
  if (verbose) {
    print(savefits)
    print(paste("min = ", cdf(interval[1], means = masses, sds = sds, weights = weights),
                " max = ", cdf(interval[2], means = masses, sds = sds, weights = weights)))
    print(data.frame(t0 = resmass$root, setot = resmasserr, mean = bootmean, errstat = booterrstat,
                     booterrtot = booterrtot, booterrsys = sqrt(booterrtot^2 - booterrstat^2),
                     bias = resmass$root - bootmean, m16 = mean(boot16), m84 = mean(boot84)))
  }
  
  return(list(effmass = effmassall, savefits = savefits,
              effmassfit = list(t0 = resmass$root, se = resmasserr, m16 = res16$root, m84 = res84$root),
              boot = list(m50 = bootmass, m16 = boot16, m84 = boot84, mean = bootmean, errstat = booterrstat, errtot = booterrtot)))
  
  
}
```

```{r}
mindistance <- 5
start <- 5
boot.R <- 1000
boot.l <- 5
afmE112 <- 0.04891 #fm
amevE112m1 <- 197.3269804/afmE112
amevE112 <- afmE112/197.3269804
```
```{r, eval=T}
pi_ss <- readcffrompreprocessed(realfile="pi.dat", path="/home/gross/Documents/heavymesons/data/meson/cE211.044.112/4Pts_meson_data/")
pi_sl <- readcffrompreprocessed(realfile="pi_sl.dat", path="/home/gross/Documents/heavymesons/data/meson/cE211.044.112/4Pts_meson_data/")

pi_ss <- bootstrap.cf(pi_ss, boot.R=boot.R, boot.l=boot.l)
pi_ss_mass <- bootstrap.effectivemass(pi_ss)
pi_ss_aic <- deteffmassaic(pi_ss_mass, start=start, mindistance = mindistance)
pi_sl <- bootstrap.cf(pi_sl, boot.R=boot.R, boot.l=boot.l)
pi_sl_mass <- bootstrap.effectivemass(pi_sl)
pi_sl_aic <- deteffmassaic(pi_sl_mass, start=start, mindistance = mindistance)

saveRDS(pi_ss_aic, file="pi_ss_aic_E112.RDS")
saveRDS(pi_sl_aic, file="pi_sl_aic_E112.RDS")
saveRDS(pi_ss_mass, file="pi_ss_mass_E112.RDS")
saveRDS(pi_sl_mass, file="pi_sl_mass_E112.RDS")
```

## Mass determination

We determine the mass of the pion in the E112 lattice by using the aic procedure on effectivemass-fits.

The masses of the valence quarks was $a\mu_{d}=0.00044$, we have measured the two-point functions of the smeared-smeared and local-smeared correlator. 
We have used 200 configurations, from 4 different replicas.

We put all replicas together, and draw from their combination.
This is justified: The autocorrelation for the masses, as determined by the uwerr analysis, for the different time slices is compatible with 0.5 in a majority of cases.
In the time slices where this is not the case, This seems to be due to fluctuations in the Gamma function.

So we can assume that the samples are not correlated, and combine all replicas.

For the analysis, we draw `r boot.R` bootstrapsamples with a binning size of `r boot.l`.

With the AIC, we determine the statistical error, and the combined error, which includes the systematical error from choosing the plateau region.

We propose all fits starting from a time distance of `r start` lattice units, including at least `r mindistance` points in the fit.

In converting the masses to MeV, we do not take the error of the lattice spacing into account. This will introduce a further systematical error.

We assume the lattice spacing to be `r afmE112` fm, as in the tau decay paper.

```{r}
pi_ss_aic <- readRDS("pi_ss_aic_E112.RDS")
pi_sl_aic <- readRDS("pi_sl_aic_E112.RDS")
pi_ss_mass <- readRDS("pi_ss_mass_E112.RDS")
pi_sl_mass <- readRDS("pi_sl_mass_E112.RDS")
afmE112 <- 0.04891 #fm
amevE112m1 <- 197.3269804/afmE112

res <- data.frame(name=c(), amass=c(), damassstat=c(), damasstot=c())

## smeared-smeared
plotwitherror(x=pi_ss_mass$t.idx, 
              y=pi_ss_mass$effMass*amevE112m1, 
              dy=pi_ss_mass$deffMass*amevE112m1, 
     xlab="t/a", ylab="m [MeV]", 
     main="smeared-smeaered pion",
     ylim=(pi_ss_aic$effmassfit$t0 + c(-1, 1)*3*pi_ss_aic$effmassfit$se)*amevE112m1)
pcol1 <- col2rgb("red", alpha = TRUE) / 255
pcol1[4] <- 0.65
pcol1 <- rgb(red = pcol1[1], green = pcol1[2],
             blue = pcol1[3], alpha = pcol1[4])
pcol2 <- col2rgb("blue", alpha = TRUE) / 255
pcol2[4] <- 0.35
pcol2 <- rgb(red = pcol2[1], green = pcol2[2],
            blue = pcol2[3], alpha = pcol2[4])
polygon(x=c(-100, 200, 200, -100),
        y=(pi_ss_aic$effmassfit$t0+pi_ss_aic$effmassfit$se*c(-1, -1, 1, 1))*amevE112m1, 
        col=pcol1, lty = 0, lwd = 0.001, border = pcol1)
polygon(x=c(-100, 200, 200, -100),
        y=(pi_ss_aic$effmassfit$t0+sd(pi_ss_aic$boot$m50)*c(-1, -1, 1, 1))*amevE112m1, 
        col=pcol2, lty = 0, lwd = 0.001, border = pcol2)
plotwitherror(x=pi_ss_mass$t.idx, y=pi_ss_mass$effMass*amevE112m1, dy=pi_ss_mass$deffMass*amevE112m1, rep=TRUE)
lines(x=c(-100, 200), y=rep(pi_ss_aic$effmassfit$t0*amevE112m1, 2), lwd=2, lty=2)
legend(x="topright", legend=c("meas", "comb", "stat"), 
       fill=c(NA, pcol1, pcol2), border=c(NA, pcol1, pcol2), 
       pch=c(1, NA, NA), co=c(1, NA, NA))

res <- rbind(res, data.frame(name="smeared-smeared", amass=pi_ss_aic$effmassfit$t0, damassstat=sd(pi_ss_aic$boot$m50), damasscomb=pi_ss_aic$effmassfit$se))

## smeared-local
plotwitherror(x=pi_sl_mass$t.idx, 
              y=pi_sl_mass$effMass*amevE112m1, 
              dy=pi_sl_mass$deffMass*amevE112m1, 
     xlab="t/a", ylab="m [MeV]", 
     main="smeared-local pion",
     ylim=(pi_sl_aic$effmassfit$t0 + c(-1, 1)*3*pi_sl_aic$effmassfit$se)*amevE112m1)
pcol1 <- col2rgb("red", alpha = TRUE) / 255
pcol1[4] <- 0.65
pcol1 <- rgb(red = pcol1[1], green = pcol1[2],
             blue = pcol1[3], alpha = pcol1[4])
pcol2 <- col2rgb("blue", alpha = TRUE) / 255
pcol2[4] <- 0.35
pcol2 <- rgb(red = pcol2[1], green = pcol2[2],
            blue = pcol2[3], alpha = pcol2[4])
polygon(x=c(-100, 200, 200, -100),
        y=(pi_sl_aic$effmassfit$t0+pi_sl_aic$effmassfit$se*c(-1, -1, 1, 1))*amevE112m1, 
        col=pcol1, lty = 0, lwd = 0.001, border = pcol1)
polygon(x=c(-100, 200, 200, -100),
        y=(pi_sl_aic$effmassfit$t0+sd(pi_sl_aic$boot$m50)*c(-1, -1, 1, 1))*amevE112m1, 
        col=pcol2, lty = 0, lwd = 0.001, border = pcol2)
plotwitherror(x=pi_sl_mass$t.idx, y=pi_sl_mass$effMass*amevE112m1, dy=pi_sl_mass$deffMass*amevE112m1, rep=TRUE)
lines(x=c(-100, 200), y=rep(pi_sl_aic$effmassfit$t0*amevE112m1, 2), lwd=2, lty=2)
legend(x="topright", legend=c("meas", "comb", "stat"), 
       fill=c(NA, pcol1, pcol2), border=c(NA, pcol1, pcol2), 
       pch=c(1, NA, NA), co=c(1, NA, NA))

res <- rbind(res, data.frame(name="smeared-local", amass=pi_sl_aic$effmassfit$t0, damassstat=sd(pi_sl_aic$boot$m50), damasscomb=pi_sl_aic$effmassfit$se))

res$damasssys <- sqrt(res$damasscomb^2-res$damassstat^2)
res$massmev <- res$amass*amevE112m1
res$dmassstatmev <- res$damassstat*amevE112m1
res$dmasscombmev <- res$damasscomb*amevE112m1

res$dmasssysmev <- sqrt(res$dmasscombmev^2-res$dmassstatmev^2)
knitr::kable((res))
write.table(x=res, file="resultspiE112.csv", row.names=F)
```
```{r}
res <- read.table("resultspiE112.csv", header=T)
# res
afm <- 0.04891
dafm <- 0.00006
res$dmasstotmev <- sqrt((dafm/afm)^2+(res$damasscomb/res$amass)^2)*res$massmev 
res$dmassspacemev <- dafm/afm*res$massmev
errorsum <- res$dmassspacemev[1] + res$dmassstatmev[1] + res$dmasssysmev[1] 
# res
# dafm/afm
# sqrt((dafm/afm)^2+(res$damasscomb[1]/res$amass[1])^2)
# sqrt((dafm/afm)^2+(res$damasscomb[1]/res$amass[1])^2)*res$massmev[1]
# dafm/afm*res$massmev[1]
# sqrt(((dafm/afm)^2+(res$damasscomb[1]/res$amass[1])^2)*res$massmev[1]^2 - res$dmasscombmev[1]^2)
```

### Error from error of the lattice spacing:

In the tau paper, the E-lattice spacing is given as `r tex.catwitherror(afm, dafm, with.dollar=F, with.cdot=F)`, meaning the relative error is `r format(dafm/afm, digits=3)`. 

We divide by the lattice spacing to get the mass in physical units.
Assuming we can use Gaussian error propagation, the error propagates together with the error from the mass (using the systematical error here) to become a total relative error of `r format(sqrt((dafm/afm)^2+(res$damasscomb[1]/res$amass[1])^2), digits=3)`.

The error from the lattice spacing leads to a further error of `r format((dafm/afm)*res$massmev[1], digits=3)` MeV.

## Combined result

Overall, we have a total result of `r tex.catwitherror(res$massmev[1], res$dmasstotmev[1], with.dollar=F, with.cdot=F, digits=2)`MeV. The errors are statistical (`r format(res$dmassstatmev[1], digits=3)`MeV, `r format((res$dmassstatmev[1]/errorsum)*100, digits=3)`%), systematical from choosing the boundaries of the plateaus (`r format(res$dmasssysmev[1], digits=3)`MeV, `r format((res$dmasssysmev[1]/errorsum)*100, digits=3)`%) and systematical from the error of the lattice spacing (`r format(res$dmassspacemev[1], digits=3)`MeV, `r format((res$dmassspacemev[1]/errorsum)*100, digits=3)`%).


<!-- <!-- distribution of the single weights: --> -->
<!-- ```{r, include=FALSE} -->
<!-- print("hi") -->
<!-- pi_ss_aic <- readRDS("pi_ss_aic_E112.RDS") -->
<!-- hist(log(pi_ss_aic[["savefits"]][["weight"]][pi_ss_aic[["savefits"]][["weight"]]>1e-20]), main = "order of magnitude of weight") -->
<!-- max(pi_ss_aic[["savefits"]][["weight"]]) -->

<!-- heat <- matrix(NA, nrow=110, ncol=110) -->
<!-- for(t1 in unique(pi_ss_aic$savefits$t1)) { -->
<!--   heat[t1, (t1+mindistance):110] <- pi_ss_aic$savefits$weight[pi_ss_aic$savefits$t1==t1] -->
<!-- } -->
<!-- heat[heat==0] <- NA -->
<!-- heatmap(log(heat), na.rm=TRUE, Rowv = NA, Colv = NA) -->
<!-- ``` -->


