---
title: "Systematic error from quark mass uncertainty"
author: "Christiane"
date: "2024-06-14"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("hadron")
```

## Background 

```{r}
nconfig <- 300
amus <- 0.01692
damus <- 0.00031
amuc <- 0.2368
damuc <- 0.0036
amud <- 0.00072
amusnew <- 0.019
amusst <- amusnew
```


We input a fixed quark mass ($a\mu$) for all calculations of the 2 and 4 point functions. However, these masses also have an uncertainty.
The usual way to quantify this is to do simulations at two different fixed quark masses and then determine the slope between the two different results. With the slope and the error of the quark mass we can determine the additional error of the correlator.

As a new strategy, we want to try inputing `r nconfig` different quark masses instead of one fixed mass.
The quark masses are sampled from a normal distribution with mean $a\mu$ and standard deviation $a\Delta \mu$.

Usually, we have one seed for the stochastic sources, which is used to produce all sources for all `r nconfig` configs.
Here, we have to submit the jobs and input scripts in a different way, so we set a different seed for the stochastic sources for each configuration.

We analyse `r nconfig` configurations of the cB211.072.48 ensemble at physical pion mass, with $a\mu_s=$ `r tex.catwitherror(x=amus, dx=damus, digits=2, with.dollar=F, with.cdot=F)` and $a\mu_c=$ `r tex.catwitherror(x=amuc, dx=damuc, digits=2, with.dollar=F, with.cdot=F)`.
$a\mu_d$ is kept fixed for both sets of analysis at $a\mu_d=$ `r sprintf("%.5f", amud)`.

We expect the means of the mesons masses and effective masses to be the same, but for the errors to be larger in the case where the quark mass was varied, so for the $D_s$, $D$, $K$ and $\eta_s$. The error should be the same for the pion.

Because we use the same sources for both measurements, we expect the pion to be identical.

Additionally, we run simulations where we change the quark mass, but it is till the same for all configurations. 
The changed quark masses we use are $a\mu_s=0.019$ and $a\mu_c=0.26$

Here, we consider the kaon in detail, and thus neglect the change in charm quark mass.
We compare in detail the results of the two different methods.


```{r defineinfos}
# After preprocessing the data for the mesons, ... we have the real 
# and imaginary parts of the correlators in one file each. 
# We read those into a cf object.
# the imaginary data need not be given.

readcffrompreprocessed <- function (realfile, path  = "", imfile="", im=F, sym=T) {
  ## determine number of measurements
  nmeas <- read.table(paste0(path, realfile), nrows=1)
  Time <- nmeas$V2
  confno <- nmeas$V1
  dat <- read.table(paste0(path, realfile), skip=1)
  tmp <- matrix(data=dat$V2, nrow=Time, ncol=confno)
  # print(nmeas)
  #~   print(tmp)
  Dm <- dim(tmp)
  ret <- cf_meta(nrObs = 1, Time =  Time, nrStypes = 1)
  if (im==F) ret <- cf_orig(ret, cf = t(tmp))
  if (im==T) {
    stopifnot(file.exists(paste0(path, imfile)))
    datim <- read.table(paste0(path, imfile), skip=1)
    tmpim <- matrix(data=datim$V2, nrow=Time, ncol=confno)
    ret <- cf_orig(ret, cf = t(tmp), icf=t(tmpim))
  }
  ret$conf.index <- confno
  if(sym) ret <- symmetrise.cf(ret)
  
  return(invisible(ret))
}


tab <- read.table(file="tableboundaries_vary_quark_masses.csv", header=T, sep=",")
## adjust the boundaries so that they are calculated for the same time slices as in the HLT algorithm
tab$t1 <- tab$t1 - 1
tab$t2 <- tab$t2 - 1
# knitr::kable(tab)

ensinfos <- data.frame(ens=c("cB211.07.48_novariation", 
                             "cB211.07.48_strange", 
                             "cB211.07.48_vary"), 
                       name=c("B48_static", "B48_strange", "B48_vary"), 
                       afm=c(0.07957, 0.07957, 0.07957), 
                       uplim=c(5, 5, 5), lowlim=c(10, 10, 10), 
                       kappa=c(0.1394265, 0.1394265, 0.1394265),
                       amu_d = c(0.00072, 0.00072, 0.00072), 
                       amu_s = c(0.01692, 0.019, 0.01692), 
                       amu_c = c(0.2368, 0.2368, 0.2368), 
                       L=c(48, 48, 48), 
                       B_ens=c(T, T, T))
numberens <- length(ensinfos$ens)
fmtogev <- 1/0.197
knitr::kable(ensinfos)

res <- data.frame(ens=c(), name=c(), amass=c(), damass=c(), massgev=c(), dmassgev=c())
reslist <- list(K=list(), 
                info=data.frame(name=rep(NA, numberens), 
                                afm=rep(NA, numberens), L=rep(NA, numberens), B_ens=rep(NA, numberens)))

```

```{r masssingle, eval=T}
index <- 1
plot <- T
normdist <- data.frame(name=c(), ens=c(), time=c(), pcorr=c(), pmass=c())
# for (ens in c("cB211.07.48")) {
for (ens in ensinfos$ens) {
  # print(ens)
  reslist[["info"]]$name[index] <- ensinfos$name[ensinfos$ens==ens]
  reslist[["info"]]$afm[index] <- ensinfos$afm[ensinfos$ens==ens]
  reslist[["info"]]$L[index] <- ensinfos$L[ensinfos$ens==ens]
  reslist[["info"]]$B_ens[index] <- ensinfos$B_ens[ensinfos$ens==ens]
  for (name in c("K")) {
    # print(name)
    if(plot) pdf(paste0("plotsnormaldistribution/distribution", ens, name, ".pdf"), title="")
    # print(system(sprintf("ls ~/Documents/heavymesons/data/meson/%s/4Pts_meson_data/%s.dat", ens, name)))
    meson <- readcffrompreprocessed(realfile=sprintf("~/Documents/heavymesons/data/meson/%s/4Pts_meson_data/%s.dat", ens, name))
    datmeff <- t(apply(X=meson$cf, MARGIN=1, FUN=effectivemass.cf, Thalf=meson$Time/2, tmax=meson$Time/2))
    for(time in seq(1, meson$Time/2)) {
      newlinenorm <- data.frame(name=name, ens=ens, time=time, 
                                pcorr=shapiro.test(meson$cf[, time])$p.value, 
                                pmass=shapiro.test(datmeff[, time])$p.value)
      normdist <- rbind(normdist, newlinenorm)
      if(plot) {
        # qqnorm(meson$cf[, time], main=paste("correlator, time =", time, ", p =", newlinenorm$pcorr))
        # qqline(meson$cf[, time])
        qqnorm(datmeff[, time], main=paste("mass, time =", time, ", p =", newlinenorm$pcorr))
        qqline(datmeff[, time])
      }
    }
    if (plot) dev.off()
    meson <- bootstrap.cf(meson, boot.R = 1000)
    # meson <- jackknife.cf(meson)
    meson <- bootstrap.effectivemass(meson)
    meson <- fit.effectivemass(meson, t1=tab$t1[tab$ensemble==ens & tab$name==name], t2=tab$t2[tab$ensemble==ens & tab$name==name])
    # print(paste("fit region", tab$t1[tab$ensemble==ens & tab$name==name], tab$t2[tab$ensemble==ens & tab$name==name],
    # "chi^2_red", sprintf("%.3f", meson$effmassfit$chisqr/meson$effmassfit$dof)))
    # plotregion <- na.omit(meson$effMass[ensinfos$lowlim[ensinfos$ens==ens]:(meson$Time/2-ensinfos$uplim[ensinfos$ens==ens])])
    # plot(meson, xlab="t/a", ylab="ameff",
    #      ylim=c(min(plotregion), max(plotregion)), main=paste(name, ensinfos$name[ensinfos$ens==ens]))
    newline <- data.frame(ens=ens, name=name, amass=meson$effmassfit$t0[1], damass=meson$effmassfit$se[1],
                          massgev=meson$effmassfit$t0[1] / ensinfos$afm[ensinfos$ens==ens] / fmtogev,
                          dmassgev=meson$effmassfit$se[1] / ensinfos$afm[ensinfos$ens==ens] / fmtogev)
    res <- rbind(res, newline)
    reslist[[name]][[index]] <- meson
  }
  index <- index + 1
}
respretty <- data.frame(ens=res$ens, name=res$name, 
                        amass=apply(X=array(c(res$amass, res$damass), dim=c(length(res$amass), 2)), 
                                    FUN=tex.catwitherror, MARGIN=1, with.cdot=FALSE, with.dollar=FALSE, digits=3), 
                        massgev=apply(X=array(c(res$massgev, res$dmassgev), dim=c(length(res$massgev), 2)), 
                                      FUN=tex.catwitherror, MARGIN=1, with.cdot=FALSE, with.dollar=FALSE, digits=3))


knitr::kable(respretty)
write.table(x=res, file="kaon_change_quark_mass.csv", row.names=FALSE)
saveRDS(object=reslist, file="kaon_change_quark_mass.RDS")
# normdist

```

The masses of the static, default quark mass and the varied quark mass are marginally compatible.

The error in the varied measurement increases by roughly 10%.

We see similar effects for the effective mass of every timeslice.

The mass of the varied set of measurements is lower than the mass of the defaukt measurement for all timeslices.


```{r masscombined}
res <- read.table("kaon_change_quark_mass.csv", header=T)
reslist <- readRDS("kaon_change_quark_mass.RDS")
names <- c("K")
limits <- data.frame(meson=c("K"), 
                     lower=rep(9, 1), 
                     upper=rep(15, 1),
                     spread=rep(5, 1))
par(mai = c(1.02, 0.8, 0.32, 0.8))
colors <- c(1, 2, 3, 4, 5, 6)
for (name_id in seq_along(names)) {
  name <- names[name_id]
  masses <- c()
  for (i in seq(1, length(reslist$info$name))) {
    masses <- append(masses, 
                     reslist[[name]][[i]]$effMass[ensinfos$lowlim[i]:(reslist[[name]][[i]]$Time/2-ensinfos$uplim[i])])
    
  }
  
  plotwitherror(x=reslist[[name]][[1]]$t.idx, 
                y=reslist[[name]][[1]]$effMass, 
                dy=reslist[[name]][[1]]$deffMass, 
                xlab="t/a", ylab="am_eff ", main=name, col=colors[1], pch=colors[1],
                xlim=c(10, 48), ylim=range(masses))
  for (i in seq(2, length(reslist$info$name))) {
    plotwitherror(x=reslist[[name]][[i]]$t.idx, 
                  y=reslist[[name]][[i]]$effMass, 
                  dy=reslist[[name]][[i]]$deffMass, 
                  pch=colors[i], col=colors[i], rep=TRUE)
  }
  lines(x=rep(unique(tab$t1[tab$name==name]), 2), y=c(-10, 100), lwd=2, lty=2)
  lines(x=rep(unique(tab$t2[tab$name==name]), 2), y=c(-10, 100), lwd=2, lty=2)
  legend(x="topright", legend=reslist$info$name, col=colors, pch=colors, inset = c(-0.14, 0), xpd=TRUE)
  print("")
}
# limits
```

```{r}

res <- read.table("kaon_change_quark_mass.csv", header=T)
# res
differences <- data.frame(name=c("amus", "amuc"), differencesigmastrange=c((0.019-amus)/damus, 0),
                          differencerelstrange=c(2*(0.019-amus)/(0.019+amus), 0))
for(name in c("K")){
  mask1 <- res$name==name & res$ens=="cB211.07.48_novariation"
  mask2 <- res$name==name & res$ens=="cB211.07.48_strange"
  newline <- data.frame(name=name, 
                        differencesigmastrange=(res$amass[mask1]-res$amass[mask2])/(res$damass[mask1]+res$damass[mask2]), 
                        differencerelstrange=2*(res$amass[mask1]-res$amass[mask2])/(res$amass[mask1]+res$amass[mask2]))
  differences <- rbind(differences, newline)
}
differences$quarkcontent=c("", "", "ds")
knitr::kable(differences, digits = 3)
```

The varied quark masses we input do not exactly reproduce the mean, there is a slight deviation. 
This might be the reason the effective masses are lower.

```{r}
fnlin <- function(par, x, boot.r) par[1]*x + par[2]
mypredict <- function(x, pararray, fn, par) {
  val <- do.call(fnlin, c(list(par = par, x = x, boot.r = 0)))
  prediction <- list(x = x, val = val)
  
  prediction_boot_fn <- function (boot.r) {
    par <- pararray[boot.r, 1:2, drop = FALSE]
    do.call(fnlin, c(list(par = par, x = x, boot.r = boot.r)))
  }
  prediction_boot <- do.call(rbind, lapply(1:nrow(pararray), prediction_boot_fn))
  prediction$boot <- prediction_boot
  
  err <- apply(prediction_boot, 2, sd, na.rm = TRUE)
  stopifnot(length(err) == length(x))
  prediction$err <- err
  return(prediction)
}

res <- read.table("kaon_change_quark_mass.csv", header=T)
reslist <- readRDS("kaon_change_quark_mass.RDS")
inputmasses <- read.table("~/Documents/heavymesons/Inclusive-heavy-decays/cB211.072.48/marvin/different_strange_masses/usedmasses_seed_1234.csv", header=TRUE)
inputmasses <- inputmasses[1:300, ]
inputmean <- mean(inputmasses$mus)
inputsd <- sd(inputmasses$mus)


bsamples <- array(NA, dim=c(1000, 2))
bsamples[, 1] <- reslist$K[[1]]$effmassfit$t[,1]
bsamples[, 2] <- reslist$K[[2]]$effmassfit$t[,1]
m <- (res$amass[1]-res$amass[2]) / (amus-amusnew)
n <- res$amass[1] - m*amus
mbs <- (bsamples[, 1] - bsamples[, 2]) / (amus-amusnew)
nbs <- bsamples[, 1] - mbs*amus
parsbs <- array(c(mbs, nbs), dim=c(1000, 2))
xseq <- seq(0.0164, 0.0195, 0.001)
prediction <- mypredict(x=xseq, pararray = parsbs, par = c(m, n), fn=fnlin)


polyval <- c(prediction$val + prediction$err, rev(prediction$val - prediction$err))
pcol <- col2rgb("black", alpha=TRUE)/255 
pcol[4] <- 0.2
pcol <- rgb(red=pcol[1],green=pcol[2],blue=pcol[3],alpha=pcol[4])
plot(x=xseq, y=prediction$val, col=1, type="l", xlab="amus", ylab="amass")
polygon(x=c(xseq, rev(xseq)), y=polyval, col=pcol, lty=0, lwd=0.001, border=pcol)
lines(x=xseq, y=prediction$val, col=1)
plotwitherror(x=c(amus, amusnew, inputmean), dx=c(0, 0, inputsd), y=res$amass, dy=res$damass, rep=T, col=c(1, 1, 2))
legend(x="topleft", legend=c("static mass, slope", "varied mass, not considered"), col=c(1, 2), pch=c(1,2))

plot(x=xseq, y=prediction$val, col=1, type="l", xlab="amus", ylab="amass", xlim=c(0.0168, 0.017), ylim=c(0.192, 0.1935))
polygon(x=c(xseq, rev(xseq)), y=polyval, col=pcol, lty=0, lwd=0.001, border=pcol)
lines(x=xseq, y=prediction$val, col=1)
plotwitherror(x=c(amus, amusnew, inputmean), dx=c(0, 0, inputsd), y=res$amass, dy=res$damass, col=c(1, 1, 2), rep=T)
legend(x="topleft", legend=c("static mass, slope", "varied mass, not considered"), col=c(1, 2), pch=c(1,2))
```

We calculate the additional error on the quark masses from the two methods:

The first method gives us:

```{r}

res <- read.table("kaon_change_quark_mass.csv", header=T)
res <- res[res$name=="K", ]
reslist <- readRDS("kaon_change_quark_mass.RDS")
resst <-res[res$ens=="cB211.07.48_strange", ]
res <- res[res$ens=="cB211.07.48_novariation", ]
stopifnot(res$name == resst$name)
booterr <- data.frame(slopestboot=c(), sslopestboot=c())
# datboot$info
for(name in c("K")) {
  reslistst <- reslist[[name]][[which(reslist$info$name=="B48_strange")]]$effmassfit$t[, 1]
  reslistnv <- reslist[[name]][[which(reslist$info$name=="B48_static")]]$effmassfit$t[, 1]
  newline <- data.frame(slopestboot=mean((reslistnv - reslistst)/(amus-amusst)),
                        dslopestboot=sd((reslistnv - reslistst)/(amus-amusst)))
  booterr <- rbind(booterr, newline)
}
# booterr
emqmone <- data.frame(name=res$name, mean=res$amass, sd=res$damass, 
                      slopest = (res$amass-resst$amass)/(amus - amusst))
emqmone <- cbind(emqmone, booterr)
emqmone$sdst = abs(emqmone$slopest) * damus
emqmone$sdstboot = abs(emqmone$slopestboot) * damus
emqmone$sdsdstboot = abs(emqmone$dslopestboot) * damus
errormesonquarkmassone <- emqmone
errormesonquarkmassone
```

From the second method we get:


```{r}
res <- read.table("kaon_change_quark_mass.csv", header=T)
res <- res[res$name=="K", ]
resvar <-res[res$ens=="cB211.07.48_vary", ]
res <- res[res$ens=="cB211.07.48_novariation", ]
stopifnot(res$name == resvar$name)
errormesonquarkmasstwo <- data.frame(name=res$name, mean=res$amass, sd=res$damass, sdvar=resvar$damass, sdquark=sqrt(resvar$damass^2-res$damass^2))
knitr::kable(errormesonquarkmasstwo, digits=5)
write.table(errormesonquarkmasstwo, file="errorquarkmassone.csv", col.names=T, row.names=F)
ratio <- errormesonquarkmasstwo$sdquark/errormesonquarkmassone$sdst
```

The first method leads to an additional error of `r tex.catwitherror(x=errormesonquarkmassone$sdst, dx=errormesonquarkmassone$sdsdstboot, digits=1, with.dollar=F, with.cdot=F)`

The second method leads to an additional error of `r format(errormesonquarkmasstwo$sdquark, digits=2)`. 
This is only `r format(ratio*100, digits=2)` % of the error from the first method.


